Price of Anarchy for Mean Field Games

### 2018-07-30 PoA.tex
fix reference in numerical results

The results show various limiting behaviors, such as some of the cases proved in the previous section. In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed. For all three cases, we see that $\lim_{b_1 \to 0}PoA >1$ and $\lim_{\bar{b}_1 \to 0}PoA=>1$. We also see that $\lim_{b_1 \to \infty}PoA = 1$ and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$. Proposition \ref{prop:b2} is confirmed in Figure \ref{fig:b2_b2bar}. When there is only interaction through the states, then $\bar{b}_2=0$ and we see that $PoA \to 1$ as $b_2 \to 0$. When there is full interaction or only interaction through the controls, then $\bar{b}_2\neq0$ and we see that $\lim_{b_2 \to 0}PoA>1$. For all three cases, we note that the condition $\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)}$ is satisfied, and thus, $\lim_{b_2 \to \infty}PoA= 1$. For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$. Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.

>>>>

The results show various limiting behaviors, such as some of the cases proved in the previous section. In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed. For all three cases, we see that $\lim_{b_1 \to 0}PoA >1$ and $\lim_{\bar{b}_1 \to 0}PoA=>1$. We also see that $\lim_{b_1 \to \infty}PoA = 1$ and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$. Propositions \ref{prop:b2_to_infty} and \ref{prop:b2_to_0} are confirmed in Figure \ref{fig:b2_b2bar}. When there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$. When there is full interaction or only interaction through the controls, then $\bar{b}_2\neq0$ and we see that $\lim_{b_2 \to 0}PoA>1$. For all three cases, we note that the condition $\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)}$ is satisfied, and thus, $\lim_{b_2 \to \infty}PoA= 1$. For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$. Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.
